
\subsubsection*{CLPU team members}

Due to administrative reasons, not all the scientists of CLPU can be part of the project as full time participants. Because of the way work is done at CLPU, all the scientific department will participate both in the work to be done as well as in the know-how needed to elaborate all the experiments.

The CLPU working team includes the next scientists, all holding a PhDs in physics:

\begin{enumerate}

\item {\bf Alicia V\'azquez Carpentier (IP of the BaTa subproject):} PhD in Physics. Scientist at CLPU since March 2014. Expert in
laser-matter interaction.

%\item {\bf Luis Roso Franco:} PhD in Physics and Professor at the University of Salamanca. Director of CLPU.  

%\item {\bf \'Alvaro Peralta Conde:} PhD in Physics. Head of the Scientific Division of CLPU. Expert in laser-matter interaction.

\item {\bf Mauricio Rico:} PhD in Physics. Specialized scientist at CLPU since June 2012. Great experience in the
design and construction of laser sources and in condense matter physics.

\item {\bf Jon I. Api\~naniz Aginako:} PhD in Physics. Scientist at CLPU since July 2013. Expert in
laser-plasma interactions.

\item {\bf Marina S\'anchez Albaneda:} PhD in Physics. Postdoctoral researcher of the University of
Salamanca working at CLPU since June 2012. Expert in laser-matter interaction in the femtosecond
timescale.

%\item {\bf Francisco Valle Brozas:} MSc in Physics and Laser Technology, and computer technical Engineer. Predoctoral fellow at CLPU since April 2013.

\end{enumerate}

It is important to mention that, additionally to the above described working team, CLPU will provide any technical or human resource needed for the satisfactory achievement of the objectives described in this proposal, as well as the know-how of the rest of the scientific department, as was mentioned before.  


