
\subsubsection*{List of companies with an interest on the project.}

The scientific and technical know-how developed for this project can be spread onto multiple industrial applications. Several companies have shown their interest on the collaboration related to the infrastructure that will be developed in this project. 

\begin{itemize}
 \item \textbf{SENER: http://www.sener.es/home/en}
SENER is a spanish engineering corporation. It works in several main branches (aerospace, infrastructures and transport, energy and marine engineering). It could be interested on both the scientific and the technical results of the project. 

\item \textbf{VALEO: http://www.valeo.com/} 
VALEO is an international corporation of automotive supplies. One of its branches is located in Spain, (VALEO Iluminaci\'on S.A.) and is specialized on automotive illumination. This corporation is currently on collaboration with the CLPU. A 4.1 micron laser has interesting transmission properties in dispersive media (fog) which could be appealing for developing automotive-related technology. 

\item \textbf{TECNATOM: http://www.tecnatom.es/}
TECNATOM is a Spanish company specialized on nuclear engineering service. It has also recently diversified their service to aeronautics, energy, transport and aerospace. It has already contacted the CLPU in order to discuss future collaborations. It has a work line of development of non-destructive diagnostics systems based on laser ultrasound generation. The infrared lasers are interesting for ultrasound generation due to their laser/matter interaction properties. 
   

\end{itemize}
