
\subsubsection*{Impact of the objectives of the CLPU subproject}

The development of a 4.1 micron laser has multiple scientific, technical and industrial applications. It can be applied on medical fields, defense, sensing and research. 

MEDICAL APPLICATIONS: The laser/tissue interaction properties of this laser is specially interesting in medicine due to the high absorbance of water in this region. The laser penetration depth is very low, it belongs to the so-called eye-safe zone because the radiation is fully absorbed in the aqueous humor of the eye. This low penetration capability allows the use of these lasers for high precision skin or circulatory-system surgery.
Journal of Optical Technology, Vol. 77, Issue 1, pp. 6-17 (2010)

DEFENSE APPLICATIONS: Mid infrared lasers have already caught the interest of the defense research community because they offer the possibility of creating countermeasures for heat-seeking missiles (whose targetry systems operate in the same wavelength range). 

SCIENTIFIC APPLICATIONS: Mid-infrared lasers are interesting in spectroscopy applications. They are as well useful as seeding or pumping lasers for mid-infrared Optical Parametric Oscillators (OPAS) 

REMOTE SENSING APPLICATIONS: The 3-5 micron window is very interesting from this point of view because a large number of important gases have absorption lines in this region (methane, nitric oxide, carbon mono-dioxide or formaldehyde) and can thus be detected. In addition to this, there are many fundamental vibration modes (O-H, C-H, N-H, etc...) with strong oscillator strengths (much higher than the overtones in the near IR) which allow detection limits down to sub-ppb. 
