
\subsubsection*{Infrastructures available at the CLPU for the subproject}


The CLPU contribution to this project is focused mainly in two tasks: 
\begin{enumerate}
\item{DEVEOLPING AN EXPERIMENT TO TEST THE DESHELVING OF THE D-STATE OF BARIUM}
\item{DESIGNING AND MANUFACTURING A 4.1 MICRON LASER FOR THE N.E.X.T. EXPERIMENT}
\end{enumerate}

The CLPU will provide an important part of the required infrastructure:
 
 \begin{itemize}
    \item \textbf{Laboratory room for all the experiments:} The experiments will be fully performed at the CLPU laboratories.
    
\item \textbf{Workshop service:} The CLPU has a mechanical workshop capable of manufacturing high level designs. 

\item \textbf{Electronics workshop:} Offers general electronics service. 

\item \textbf{Auxiliary services:} KHZ amplified Ti:Saphire laser (Spitfire, Spectraphysics, 7 mJ 100 fs), laser micro-machining station, Optical and Scanning electron microscopes (ZEISS).  

\item \textbf{Data acquisition equipment:} Three oscilloscopes up to 1 GHZ (Tektronix), data acquisition computer, 3 GHZ RF spectrum analyzer (Tektronix). 

\item \textbf{Synchro and timing electronics:} Delay generator (Stanford). 

\item \textbf{Vacuum equipment:} Primary pumps, turbo-molecular pumps, general vacuum hardware.

\item \textbf{Temperature control equipment:} Thermoelectrical chiller, 

\item \textbf{Optica equipment (general, all for vis/nir):} Laser spectrum analyzer (500-1500 nm), Laser spectrum analyzer (1000-2600 nm), photodiodes (Ge, Si), ultra-fast photodiodes (300 ps), CCD cameras, two Laser Beam profilers (Gentec), optical autocorrelator (up to 50 fs, sweep), home-made optical autocorrelator (single shot), alignment lasers (HeNe), shutters, chopper (Stanford), filters, lenses, mirrors, general optomechanics (posts, post holders, clamping forks, waveplates, diaphragms, etc), two infrared viewers (up to 1350 nm), optics and optomechanics (mirrors, lenses, LBO crystals for 800 and 1030 nm, posts, clamping forks, mounts, etc.)

\item \textbf{Lasers:} a 493.54 nm CW LASER: Pump laser (Coherent, Verdi G 20 W, 532 nm, CW); a tunable Ti:Saphire laser CW (750-1020 nm,  more than 4W).

\item \textbf{Spetrometer (UV-VIS-NIR, MIGHTEX)}

\item \textbf{Power and energy meters:} thermal and pyroelectrical. 

\end{itemize}

Related to the 4.1 micron laser manufacturing we can provide optomechanics. The rest will be purchased under the project funding. 

  