% Los objetivos específicos de cada uno de los subproyectos participantes, enumerándolos brevemente, con claridad, precisión y de manera realista (acorde con la duración prevista del proyecto).
%
% En los subproyectos con dos investigadores principales, deberá indicarse expresamente de qué objetivos específicos se hará responsable cada uno de ellos.
%

\subsubsection*{Capacidad Formativa del equipo solicitante}

The CALREC sub-project requests one Ph.D student (FPI grant)

{\bf Training program}

The student will follow the Particle Physics doctorate program at USC (``programa de doctorado en F\'isica de Part\'iculas"), attend at least one international school (CERN HEP school, Gran Sasso Sciente Institute), a national one (Taller de Altas Energ\'ias) and at least two international conferences.
%The student will do his research within an international collaboration.
%The student will learn instrumentation in HEP, and high level programming and the use of mathematical method common in HEP. 
%He will work in the internacional environment of NEX. 
%He will profit from the excellent internal NEXT collaboration.
The student is expected to present regularly results in the NEXT meetings. His thesis results will be presented in a high profile international conference and will be published in a reputed international physics journal.
%pected that he will attend and present his results in the NEXT meetings.
%He will attend (at least two) international conferences or workshops, and will present this thesis results in a high level profile conference.

{\bf Ph.D. thesis}

The IP, Jose A. Hernando, has directed the following Ph.D. thesis:
\begin{enumerate}

\item Title: ``Search for the rare decays $B_s \to \mu^+\mu^-$
and $K_S \to \mu^+\mu^-$ in the LHCb with 1 fb$^{-1}$ integrated luminosity" \\
Institution: Universidade de Santiago de Compostela \\
Student: Xabier Cid Vidal \\
Date: 26/10/2012 \\
ID: CERN-THESIS-2012-154  

\item Title: ``Search for the very rare decay $B_s \to \mu^+\mu^-$ in the LHCb experiment" \\
Student: Diego Martinez Santos \\
Institution: Universidade de Santiago de Compostela \\
Date: 04/04/2010 \\
ID: CERN-THESIS-2010-068 

\end{enumerate}

{\bf Scientific career of the graduated Ph.D.s}

%Diego Mart\'inez and X. Cid have an excellent careers after finishing their Ph.D.s. 

D. Mart\'inez Santos was research fellow at CERN after he defended his Ph.D. thesis at USC. He is now postdoct at NIKHEF institute, Amsterdam, and CERN Corresponding Associate. He is the coordinator of the $B_s$ mixing phase, $\phi_s$, (the second main LHCb result after the $B_s \to \mu^+\mu^-$ search). He was awarded in 2013 with the Young Experimental Physicist Prize by the European Physical Society (EPS) for his work at the LHCb trigger and the search of the $B_s \to \mu^+ \mu^-$ decay. He has applied for a ERC (European Research Council) Starting Grant with a project based on reusing the LHCb detector to boost strange mesons physics. 
%He has successfully pass the first step of the selection process. 

X. Cid Vidal got a three-years research fellow at CERN after he defended his Ph.D thesis at the USC. He is currently working on the identification of the Higgs boson to b,b-bar jets at LHCb and leading the strange mesons physics at LHCb. He has recently presented a Marie Curie ITN  (International Training Network) proposal to extend kaon physics, and to apply multivariate methods used in HEP into other fields, for example to study the evolution of financial markets.
 


