% Los objetivos específicos de cada uno de los subproyectos participantes, enumerándolos brevemente, con claridad, precisión y de manera realista (acorde con la duración prevista del proyecto).
%
% En los subproyectos con dos investigadores principales, deberá indicarse expresamente de qué objetivos específicos se hará responsable cada uno de ellos.
%

\subsubsection*{Equipment and Infrastructures: COORD, ENG and CALREC subprojects}

\begin{enumerate}
\item {\bf A state-of-the-art laboratory at IFIC}, developed and financed with funds from CUP. The DEMO detector is operating here. The laboratory includes a full gas system, infrastructures for vacuum and high pressure operation; high voltage and slow control systems; a full DAQ and computing system. 
\item {\bf A state-of-the-art laboratory electronics laboratory at IFIC}, which has made possible the very fast development of the tracking plane. 
\item {\bf A state-of-the-art electronics laboratory at UPV}, which has made possible the very fast development of the FEE and DAQ. Of particular interest is the collaboration of UPV with CERN, in the context of RD51 collaboration, one of the main reasons why NEXT has been declared CERN recognised experiment.
\item {\bf Computation resources at the US}, where there is a large cluster (Tier2 class) 
for distributed LHCb analysis, with about 1500 processor cores. The NEXT experiment, through the PI of the CALREC subproject will have access to this cluster for Monte Carlo simulation and data reconstruction. 
\item {\bf Experimental laboratory at the US}, which 
includes a clean room (30 m$^2$ class 100000) with an automatic ultrasonic wedge bonding machine. This laboratory is ideal to set the gas-additive program to be carried out by US. 
item {\bf Infrastructures at LSC}, which include: a) working platform and seismic pedestal; b) lead castle; c) gas system; d) clean tent; e) radon suppression system. In addition, the LSC provided general support for the experiments. 
\item {\bf A state-of-the-art facility for radio purity measurements}, located at the LSC. 
\end{enumerate}

\subsubsection*{Equipment and Infrastructures: BATA subproject}

For the successful development of this subproject, CLPU will provide the required human and technological resources. CLPU is the centre of reference in Spain regarding laser technology, and takes active part in several international and national projects.  Moreover, {\bf CLPU considers this project of high priority and consequently will offer the collaboration of all the scientific department} consisting of a multidisciplinar team with broad experience in laser technology and development, and laser-matter interaction. 

The CLPU will provide a substantial part of the required infrastructure for the \BATA\ subproject, including.
 
 \begin{itemize}
    \item \textbf{Laboratory room for all the experiments:} The experiments will be fully performed at the CLPU laboratories.
    
\item \textbf{Workshop service:} The CLPU has a mechanical workshop capable of manufacturing high level designs. 

\item \textbf{Electronics workshop:} Offers general electronics service. 

\item \textbf{Auxiliary services:} KHZ amplified Ti:Saphire laser (Spitfire, Spectraphysics, 7 mJ 100 fs), laser micro-machining station, Optical and Scanning electron microscopes (ZEISS), plist DAQ services, vacuum equipment and optical equipment.   

%\item \textbf{Data acquisition equipment:} Three oscilloscopes up to 1 GHZ (Tektronix), data acquisition computer, 3 GHZ RF spectrum analyzer (Tektronix). 
%
%\item \textbf{Vacuum equipment:} Primary pumps, turbo-molecular pumps, general vacuum hardware.
%
%\item \textbf{Temperature control equipment:} Thermoelectrical chiller, 
%
%\item \textbf{Optical equipment (general, all for vis/nir):} Laser spectrum analyser (500-1500 nm), Laser spectrum analyser (1000-2600 nm), photodiodes (Ge, Si), ultra-fast photodiodes (300 ps), CCD cameras, two Laser Beam profilers (Gentec), optical autocorrelator (up to 50 fs, sweep), home-made optical autocorrelator (single shot), alignment lasers (HeNe), shutters, chopper (Stanford), filters, lenses, mirrors, general optomechanics (posts, post holders, clamping forks, waveplates, diaphragms, etc), two infrared viewers (up to 1350 nm), optics and optomechanics (mirrors, lenses, LBO crystals for 800 and 1030 nm, posts, clamping forks, mounts, etc.)

\item \textbf{Lasers:} a 493.54 nm CW LASER: Pump laser (Coherent, Verdi G 20 W, 532 nm, CW); a tunable Ti:Saphire laser CW (750-1020 nm,  more than 4W).
%
%\item \textbf{Spectrometer (UV-VIS-NIR, MIGHTEX)}
%
%\item \textbf{Power and energy meters:} thermal and pyroelectrical. 

\end{itemize}


