\subsubsection{Scientific and technological impact}

This project involves the construction of detectors which are unique in the world, implementing the HPXe technology with EL readout, widely considered as one of the most promising ones in the field of \bbonu\ searches. Therefore: 
\begin{enumerate}
\item {\bf The NEXT experiment has the potential of being at the forefront of a major scientific discovery}. The sensitivity of NEXT-100 will reach that achieved by GERDA, EXO and KamLAND-Zen by 2018, with the experiment still operating in a regime far from background saturation. Consequently, from 2018 onwards, NEXT will probe a region of \mbb\ space that is yet unexplored. If the NME is sufficiently large, NEXT could observe \bbonu\ events, thus making (or participating in the making, together with other leading experiments of the field) a major discovery.
\item {\bf The NEXT will bring innovation to the industry-science relation in Spain}. The experiment uses and develops high technology, involving national and international firms. We have written statements of interest by companies in the sectors of mechanical equipment (AIMPLAS, ACEX), gas and pressure equipment(Swagelock, SERA), and light sensors equipment (SENSL, Hamamatsu), among others. We are starting joint R\&D  projects with a number of them. Examples include radio-pure SiPMs with SENSL, UV sensitive SiPMs with Hamamatsu, and new plastic materials with AIMPLAS.  
\item {\bf Our approach to BATA is opening a new inter-disciplinary field}. Our approach incorporates elements of atomic physics, nuclear physics, particle physics, laser-matter interactions, and photonics. It involves the technology of \HPXE\ chambers, ion sources, magnetic-traps, and lasers (both visible and IR). There is a clear potential to develop experimental techniques associated to our experiments that go beyond our particular needs and have wide applications.
\end{enumerate}

\subsubsection{Dissemination of results}

The results of the experiment will be amply advertised. NEXT and CLPU keep modern web pages, and a firm presence in social media. In addition, the spokesperson of NEXT is the science-advisor of the well known JotDown magazine\footcite{JotDown}, and develops an intense outreach activity which involves interviews to scientific personalities\footcite{JotDownNygrenBettini, JotDownCattaiGonzalez, JotDownHalzen} as well as a scientific blog\footcite{JotDownBlog}.

\subsubsection{Technology transfer}

Among the potential applications, and scientific and industrial returns, we will mention:
\begin{enumerate}
\item {\bf The development of solid-state MIR laser technology}. Laser radiation in the MIR spectrum is invisible to the human eye and is not absorbed by the atmosphere, having obvious applications in the surveillance industry. At the same time, IR emission also enhances night vision equipment capabilities by flooding forward positions with invisible light that enhances light gathering performance and increasing the ability to detect objects at greater lengths. 
\item {\bf The development of matrices of sensors (SiPMs) and the associated software suitable for medical imaging.} The dense SiPM arrays used in the NEXT tracking plane, together with the associated electronics and software, may have direct applications to novel imaging systems in medicine capable of better resolution and/or operation at lower doses. This is due to the capabilities of SiPMs of reconstructing 3D positions for dim signals. 
\end{enumerate}