\subsection{Travel to LSC}
The NEW detector will be installed and commissioned at the LSC in mid 2015. In 2016, NEW will operate at the LSC, while the NEXT-100 detector will be constructed at IFIC, UPV and Texas, among other laboratories. In 2017, NEXT-100 will be commissioned at the LSC. Operation will proceed from 2018 onwards.

During commissioning, we foresee the constant presence at the LSC of one of our mechanical engineers and one of our electronics engineer (4 weeks a month).  This is a must, because IFIC and UPV jointly coordinate the mechanics, electronics and computing of NEXT. In the operation periods, when the detector is stable, this presence can be reduced to one week per month. Concerning post-docs, a constant presence of 2 post-docs or students (4 weeks a month) from our groups is needed. In addition, one student or post-doc in charge of the detector shifts is needed. We also foresee the presence of the PI and technical coordinator for about one week per month during the span of the project. 

Notice that the personnel at the LSC provided by the international collaboration will amply match the personnel provided by this project. The USA groups foresee to deploy at least two physicists to the LSC (4 weeks per month). The portuguese groups will deploy at least two more. Personnel from the University of Zaragoza, which is a part of NEXT, will travel frequently to the LSC. 

To minimise costs, we foresee to rent an apartment near Canfranc (probably at Jaca), and to organise travel car-pooling the teams. The daily expenses are computed conservatively (250 \euro\ per week). 

\begin{table}[h!]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
Activities at LSC &	2015 &	2016 &	2017 &	2018\\
 \hline	
Construction &	NEW (6 months) &	NEXT-100 & - & - \\ 		
Commissioning	&NEW (6 months) &	- & NEXT-100 & - \\	
Operation	&	- &  NEW & - & NEXT-100 \\ 	
\hline\hline	
\end{tabular}  
\caption{Activities at the LSC.}
\label{tab.ActivitiesLSC}
\end{center}
\end{table}
 
\begin{table}[h!]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
Personnel at LSC &	2015 &	2016 &	2017 &	2018\\
\hline							
engineers &	2 x 4 w/m per 6 months &	2 x 1 w/m & 2 x 4 w/m per 9 months  &	2 x 1 w/m\\
post-docs/students & 	2 x 4 w/m per 6 months &	2 x 4 w/m & 2 x 4 w/m &	2 x 4 w/m \\
Technical coordinator &	1 x 1 w/m &1 x 1 w/m &1 x 1 w/m &	1 x 1 w/m \\
PI	& 1 x 1 w/m &	1 x 1 w/m &1 x 1 w/m &	1 x 1 w/m\\
Shifters &	1 x 4 w/m per 6 months &	1 x 4 w/m	& 1 x 4 w/m & 1 x 4 w/m \\
\hline\hline
\end{tabular}  
\caption{Personnel at the LSC. w/m means week per month. }
\label{tab.PersonelLSC}
\end{center}
\end{table}

\begin{table}[h!]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
Weeks at LSC &	2015 &	2016 &	2017 &	2018\\
\hline							
engineer& 	48 &	24 &	72 &	24 \\
post-docs/students & 	48	& 96 & 	96 &	96\\
Technical coordinator &	6	& 12	 & 12	 & 12\\
PI	& 6	& 12	 & 12	 & 12\\
Shifters &	24 &	48 &	48 &	48\\
\hline
Total &	132	&192 &	240 &	192\\
\hline\hline
\end{tabular}  
\caption{Weeks at the LSC}
\label{tab.WeeksLSC}
\end{center}
\end{table}

\begin{table}[h!]
\begin{center}
\begin{tabular}{|l|c|}
\hline				
Large apartment rental (month) &	1200	\\		
car-pool trip &	150 \\			
number of car-pool trips & 1 per week \\
subsistence/week &	250 \\
\hline \hline	
\end{tabular}  
\caption{Details of costs}
\label{tab.DetailsLSC}
\end{center}
\end{table}	


\begin{table}[h!]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline	
Concept &	2015 &	2016 &	2017 &	2018\\
\hline						
Apartment	 & 7,200 &	14,400 &	14,400 &14,400 \\
Trips	& 3,600 &	6,000 &	6,000 &	6,000 \\
Subsistance &	33,000 &	48,000	& 60,000 & 48,000 \\
\hline
Total &	43,800 &	68,400 &	80,400 &	68,400 \\				
\hline \hline				
\end{tabular}  
\caption{Costs travel to the LSC.}
\label{tab.CostsLSC}
\end{center}
\end{table}

Tables \ref{tab.ActivitiesLSC}, \ref{tab.PersonelLSC},  
\ref{tab.WeeksLSC}, \ref{tab.DetailsLSC} and  \ref{tab.CostsLSC} detail the calculation of costs. The total travel to LSC foreseen during the span of this project is 261,000 \euro.


