\subsubsection*{Objectives of the COORD subproject}
The COORD subproject leads objective 1 (completion of infrastructures),
objective 3 (commissioning of NEW), and objective 7 (commissioning of NEXT-100). It co-leads, together with the ENG subproject objective 2 (NEW construction) and objective 6 (construction of NEXT-100). It co-leads objectives 4 and 7 (evaluation of performance of NEW and NEXT-100) together with CALREC and co-leads objective 9 (\BATA\ R\&D) together with CLPU.

The ENG subproject leads the development of the electronics of the NEW and NEXT-100 detector (objectives 3 and 6). Evaluation of the detector performance requires both an extensive calibration and a well tuned reconstruction, areas lead by the CALREC subproject. All the sub projects will participate in the \BATA\ R\&D. CLPU will bring in the laser technology, COORD the construction of the prototype chambers, ENG the deployment of sensors and electronics and CALREC the reconstruction of events. The participation of CLPU (BATA subproject) is essential for this objective.

Next we describe with more detail the objectives of each subproject.


The objectives of this coordinated project correspond to the Working Packages described in the NEXT Project Management Plan (PMP). Specifically: 
\begin{itemize}
\item {\bf WP1: PV (Pressure Vessel)}: Construction of the NEW and NEXT-100 pressure vessels. 
\item {\bf WP2: GS (Gas System)}: Installation and commissioning of the Gas System for NEW and NEXT-100 at the LSC. 
\item {\bf WP3:IS (Infrastructures)}: Construction of the infrastructures (working platform, seismic pedestal, lead castle, radon suppression system and clean tent), needed for the operation of NEW/NEXT-100.
\item {\bf WP4: FC (Field Cage)}: Construction of the field cage, light tube, HVFT and EL grids of NEW and NEXT-100.
\item {\bf WP5: EP (Energy plane)}: Construction of the NEW/NEXT-100 energy planes.
\item {\bf WP6: TP (Tracking plane)}: Construction of the NEW/NEXT-100 tracking planes.
\item {\bf WP7: FEE (Front-End electronics)}: Front-End electronics of energy and tracking planes.
\item {\bf WP8: DAQ (Data Acquisition )}: Data  acquisition of the energy and tracking planes.
\item {\bf WP9 ONL (Online) }: Online monitoring for NEW/NEXT-100. 
\item {\bf WP10: SLW (Slow Controls)}: Slow controls of the detectors, gas system and ancillary systems.
\item {\bf WP11: MC (Monte Carlo)}: Monte Carlo simulation of the detector(s) and implementation of the background model. 
\item {\bf WP12: REC (Reconstruction)}: Offline reconstruction of events in NEW/NEXT-100.
\item {\bf WP13: SOF (Software)}: Development and maintenance of software tools (reconstruction and analysis frameworks, release tools, software libraries) and coordination of data and Monte Carlo productions. 
\item {\bf WP14: CAL (Calibration)}: Calibration of the NEW/NEXT-100 with radioactive sources. 
\item {\bf WP15: RAD (Radiopurity)}: Screening, using the LSC facilities, as well as several other techniques, of all the components being used in the  NEW/NEXT-100 detectors. 
\end{itemize}

The COORD subproject addresses the objectives corresponding to WP1 to WP6, WP11 and WP13. The objectives of the ENG subproject are those corresponding to WP7 to WP10. The objectives of the CALREC subproject are those included in WP12 and WP14. Finally, the objectives of the RPUR subproject are those included in WP15.  
